Information is Not Communicated Uniformly: Evidence from Spoken and Written Corpora

### 2019-01-26 cogsci/position-info.Rmd
updates to Rmd

author-information: > 
    \author{{\large \bf Josef Klafka} \\ \texttt{jklafka@uchicago.edu} \\ Department of Psychology \\ University of Chicago
    \And {\large \bf Daniel Yurovsky} \\ \texttt{yurovsky@uchicago.edu} \\ Department of Psychology \\ University of Chicago}

abstract: 
    "We provide evidence against the popular Uniform Information Density hypothesis (Levy & Jaeger, 2007) which proposes that information is transmitted at a constant rate close to channel capacity in human communication. Using a method based on the original Genzel & Charniak (2002) entropy measure, we construct a word-level model for entropy applicable to both spoken and written corpora. We apply this model to corpora from Wikipedia in well over a hundred languages. We find that not only is the Uniform Information Density hypothesis prediction wrong, but also that the by-word entropy distribution of a language is related to the typological features of the language. We use this evidence to suggest that people do not communicate information at a uniform rate, but that information distribution varies from language to language based on phonogical, morphological and syntactic features."

keywords:
    "Entropy; information; information theory; communication"

output: cogsci2016::cogsci_paper
---

@@

```{r, libraries}
library(png)
library(grid)
library(ggplot2)
library(xtable)
```

# Background

Perhaps the most important reason people talk and write to one another is to give information. From Shannon (1948), we know that when information is being communicated, the rate of information transmission should be constant and as close as possible to the capacity of the communication channel to optimally transmit the information. Levy & Jaeger (2007) introduce the *uniform information density* (UID) hypothesis, arguing that people unconsciously structure their speech and writing to communicate information at a constant, optimal rate. Levy & Jaeger (2007) argue that speakers and writers should attempt to communicate information as evenly as possible and as close to the channel capacity as possible. Their evidence concerns the use or lack of use of “that”-complementizers in introducing English relative clauses. When the word preceding the relative clause or the initial word of the relative clause has high information content, then the authors argue that speakers are more likely to use the complementizer. The authors use adult-adult conversations from the Penn Treebank corpus.

UID has been applied broadly over the past decade, to determining whether linguistic alignment takes place (Jaeger & Snider, 2013), Zipfian word length distributions (Piantadosi et al., 2011), communication efficiency (Mahowald et al., 2013), dialogue and turn-taking (Xu & Reitter, 2018) and the significance of ambiguity in language (Piantadosi et al., 2012), among other research. However, other recent work has contradicted the UID hypothesis. Zhan and Levy (2018) study Mandarin Chinese classifier use for specific and general Mandarin classifiers. Specific classifiers are specific to certain nouns, and UID would predict that specific classifiers would appear when the production of the corresponding noun is easier, to spread the information contained by the classifier and noun less densely over time. General classifiers can be applied to any noun and contain no special information content. Zhan and Levy find that speakers use specific classifiers more often in cases where the production of the corresponding noun is more difficult than when the production is easier; speakers do not avoid unexpected peaks in information content for their listeners, but instead maximize their ease of production.

Similar to the original Levy & Jaeger (2007), Zhan and Levy (2018) focuses on information distribution at particular points in a sentence. By contrast, Jain et al. (2018) examine word order across spoken sentences in Hindi, a freer word order language than English, and find that information density has no significant effect on word order. For this paper, we focus on the sentence level instead of specific points, following a method described in Yu et al. (2016).

Yu et al. (2016) challenges the UID hypothesis through examining an entropy measure across sentence positions within the text portion of the English-language British National Corpus (BNC). They partition the corpus by sentence length in number of words. For each word position $X$ of sentences of length $k$, they define $w$ as a unique word occurring in position $X$. They define $p(w)$ as the number of times word $w$ occurs in position $X$ divided by the number of total words that occur in position $X$ i.e. the number of sentences of length $k$. Then $p(w)$ is the probability of obtaining word $w$ by choosing a word at random in position $X$ in sentences of length $k$.

$$H(X) = \sum\limits_w p(w)\log\big(p(w)\big)$$
With this measure, Yu et al. compute the unigram entropy at each position of sentences of each length within the corpus. The result of this method can be plotted for each utterance length as an *entropy curve*, which can be visually compared across utterance length to observe the how the unigram entropy changes across absolute positions in each of the utterances. Genzel & Charniak (2002) similarly examine a unigram entropy measure on sentences, and found that entropy at the sentence level increases linearly with sentence index within a corpus. UID applies this uniformity of entropy rate in sentences to all levels of speech, and so the Yu et al. method, which examines text at the word level, should find an affine function at the word level.

The entropy curve is a consequence of the information-theoretic rate of information transfer in a language, where information is defined as a reduction in uncertainty. Thus the more entropy at a word position in a sentence (Yu et al., 2016) or a sentence index in a text (Genzel & Charniak, 2002), the more information is on average contained around that position. Let us assume that the UID perspective is correct. Then we expect that the entropy curve for every language should be close to an affine, linear function with some noise. Entropy should monotonically and uniformly increase at all word positions across utterances on average. We will find a contradiction with this claim through examining the average entropy at each position of a sentence for both speech and text data.

@@

The UID hypothesis predicts that information transmission rate will tend towards uniformity in both speech and text. We begin by examining speech to determine if we obtain the entropy curve shape we expect for spoken communication. We begin with the same source as Levy & Jaeger (2007) and Jaeger (2010), the Switchboard corpus of adult telephone conversations. We also examine child-adult conversations in the CHILDES TalkBank (Brown 1973; MacWhinney 2014) corpora database of spoken adult-child conversations in multiple languages. Children are not fully developed speakers, so we want to compare the entropy curve we obtain by computing over the utterances in the CHILDES corpora to the utterances in the adult-adult Switchboard corpus.

@@

In the English CHILDES corpora. The entropy curves capture individual variation across positions in utterances of the same length. This allows us to directly observe and judge the amount of variation in words that appear in an individual position of a sentence. For speech data, which for the corpora in the CHILDES database consists of short and often disconnected utterances across hours of recordings, the unigram entropy measure is unaffected by context or lack thereof in utterances by the adults and children in the corpora. We can directly compare any two positions within utterances to determine the amount of uncertainty, and therefore information, on average contained by words within that position of utterances. We are applying the same approach as in Genzel and Charniak (2002), but within sentences instead of across sentences.

@@

```{r tables}
glm_model <- read.csv("glm.csv")
tab1 <- xtable::xtable(glm_model)
print(tab1, type="latex", comment = F, table.placement = "H")
```

>>>>

author-information: > 
 \author{Josef Klafka \and Daniel Yurovsky \\
         \texttt{\{jklafka, yurovsky\}@uchicago.edu} \\
        Department of Psychology \\ University of Chicago}

abstract: >
    We provide evidence against the popular Uniform Information Density hypothesis (Levy & Jaeger, 2007) which proposes that information is transmitted at a constant rate close to channel capacity in human communication. Using a method based on the original Genzel & Charniak (2002) entropy measure, we construct a word-level model for entropy applicable to both spoken and written corpora. We apply this model to corpora from Wikipedia in well over a hundred languages. We find that not only is the Uniform Information Density hypothesis prediction wrong, but also that the by-word entropy distribution of a language is related to the typological features of the language. We use this evidence to suggest that people do not communicate information at a uniform rate, but that information distribution varies from language to language based on phonogical, morphological and syntactic features.

keywords: >
    Entropy; information; information theory; communication

output: cogsci2016::cogsci_paper
#final-submission: \cogscifinalcopy
---

@@

```{r, libraries}
library(png)
library(grid)
library(tidyverse)
library(xtable)
```

Perhaps the most important reason people talk and write to one another is to give information. From @shannon1948, we know that when information is being communicated, the rate of information transmission should be constant and as close as possible to the capacity of the communication channel to optimally transmit the information. @levy2007 introduce the *uniform information density* (UID) hypothesis, arguing that people unconsciously structure their speech and writing to communicate information at a constant, optimal rate. @levy2007 argue that speakers and writers should attempt to communicate information as evenly as possible and as close to the channel capacity as possible. Their evidence concerns the use or lack of use of “that”-complementizers in introducing English relative clauses. When the word preceding the relative clause or the initial word of the relative clause has high information content, then the authors argue that speakers are more likely to use the complementizer. The authors use adult-adult conversations from the Penn Treebank corpus.

UID has been applied broadly over the past decade, to determining whether linguistic alignment takes place [@jaeger2013], Zipfian word length distributions [@piantadosi2011], communication efficiency [@mahowald2013], dialogue and turn-taking [@xu2018] and the significance of ambiguity in language [@piantadosi2012], among other research. However, other recent work has contradicted the UID hypothesis. @zhan2018 study Mandarin Chinese classifier use for specific and general Mandarin classifiers. Specific classifiers are specific to certain nouns, and UID would predict that specific classifiers would appear when the production of the corresponding noun is easier, to spread the information contained by the classifier and noun less densely over time. General classifiers can be applied to any noun and contain no special information content. Zhan and Levy find that speakers use specific classifiers more often in cases where the production of the corresponding noun is more difficult than when the production is easier; speakers do not avoid unexpected peaks in information content for their listeners, but instead maximize their ease of production.

Similar to the original @levy2007, @zhan2018 focuses on information distribution at particular points in a sentence. By contrast, @jain2018 examine word order across spoken sentences in Hindi, a freer word order language than English, and find that information density has no significant effect on word order. For this paper, we focus on the sentence level instead of specific points, following a method described in @yu2016.

@yu2016 challenges the UID hypothesis through examining an entropy measure across sentence positions within the text portion of the English-language British National Corpus (BNC, CITE). They partition the corpus by sentence length in number of words. For each word position $X$ of sentences of length $k$, they define $w$ as a unique word occurring in position $X$. They define $p(w)$ as the number of times word $w$ occurs in position $X$ divided by the number of total words that occur in position $X$ i.e. the number of sentences of length $k$. Then $p(w)$ is the probability of obtaining word $w$ by choosing a word at random in position $X$ in sentences of length $k$.

$$H(X) = \sum\limits_w p(w)\log\big(p(w)\big)$$
With this measure, @yu2016  compute the unigram entropy at each position of sentences of each length within the corpus. The result of this method can be plotted for each utterance length as an *entropy curve*, which can be visually compared across utterance length to observe the how the unigram entropy changes across absolute positions in each of the utterances. @genzel2002 similarly examine a unigram entropy measure on sentences, and found that entropy at the sentence level increases linearly with sentence index within a corpus. UID applies this uniformity of entropy rate in sentences to all levels of speech, and so the @yu2016, which examines text at the word level, should find an affine function at the word level.

The entropy curve is a consequence of the information-theoretic rate of information transfer in a language, where information is defined as a reduction in uncertainty. Thus the more entropy at a word position in a sentence [@yu2016] or a sentence index in a text [@genzel2002], the more information is on average contained around that position. Let us assume that the UID perspective is correct. Then we expect that the entropy curve for every language should be close to an affine, linear function with some noise. Entropy should monotonically and uniformly increase at all word positions across utterances on average. We will find a contradiction with this claim through examining the average entropy at each position of a sentence for both speech and text data.

@@

The UID hypothesis predicts that information transmission rate will tend towards uniformity in both speech and text. We begin by examining speech to determine if we obtain the entropy curve shape we expect for spoken communication. We begin with the same source as @levy2007 and @jaeger2010, the Switchboard corpus of adult telephone conversations. We also examine child-adult conversations in the CHILDES TalkBank [@brown1973; @macwhinney2014] corpora database of spoken adult-child conversations in multiple languages. Children are not fully developed speakers, so we want to compare the entropy curve we obtain by computing over the utterances in the CHILDES corpora to the utterances in the adult-adult Switchboard corpus.

@@

In the English CHILDES corpora. The entropy curves capture individual variation across positions in utterances of the same length. This allows us to directly observe and judge the amount of variation in words that appear in an individual position of a sentence. For speech data, which for the corpora in the CHILDES database consists of short and often disconnected utterances across hours of recordings, the unigram entropy measure is unaffected by context or lack thereof in utterances by the adults and children in the corpora. We can directly compare any two positions within utterances to determine the amount of uncertainty, and therefore information, on average contained by words within that position of utterances. We are applying the same approach as in @genzel2002, but within sentences instead of across sentences.

@@

```{r tables, results="asis", tab.env = "table"}
glm_model <- read_csv("glm.csv") %>%
    select(-X1)

tab1 <- xtable::xtable(glm_model)
print(tab1, type="latex", comment = F, table.placement = "tb",
      include.rownames = F)
```

### 2019-01-26 cogsci/position-info.tex
updates to Rmd

\author{{\large \bf Josef Klafka} \\ \texttt{jklafka@uchicago.edu} \\ Department of Psychology \\ University of Chicago \And {\large \bf Daniel Yurovsky} \\ \texttt{yurovsky@uchicago.edu} \\ Department of Psychology \\ University of Chicago}

@@

\section{Background}\label{background}

Perhaps the most important reason people talk and write to one another
is to give information. From Shannon (1948), we know that when
information is being communicated, the rate of information transmission
should be constant and as close as possible to the capacity of the
communication channel to optimally transmit the information. Levy \&
Jaeger (2007) introduce the \emph{uniform information density} (UID)
hypothesis, arguing that people unconsciously structure their speech and
writing to communicate information at a constant, optimal rate. Levy \&
Jaeger (2007) argue that speakers and writers should attempt to
communicate information as evenly as possible and as close to the
channel capacity as possible. Their evidence concerns the use or lack of
use of ``that''-complementizers in introducing English relative clauses.
When the word preceding the relative clause or the initial word of the
relative clause has high information content, then the authors argue
that speakers are more likely to use the complementizer. The authors use
adult-adult conversations from the Penn Treebank corpus.

UID has been applied broadly over the past decade, to determining
whether linguistic alignment takes place (Jaeger \& Snider, 2013),
Zipfian word length distributions (Piantadosi et al., 2011),
communication efficiency (Mahowald et al., 2013), dialogue and
turn-taking (Xu \& Reitter, 2018) and the significance of ambiguity in
language (Piantadosi et al., 2012), among other research. However, other
recent work has contradicted the UID hypothesis. Zhan and Levy (2018)
study Mandarin Chinese classifier use for specific and general Mandarin
classifiers. Specific classifiers are specific to certain nouns, and UID
would predict that specific classifiers would appear when the production
of the corresponding noun is easier, to spread the information contained
by the classifier and noun less densely over time. General classifiers
can be applied to any noun and contain no special information content.
Zhan and Levy find that speakers use specific classifiers more often in
cases where the production of the corresponding noun is more difficult
than when the production is easier; speakers do not avoid unexpected
peaks in information content for their listeners, but instead maximize
their ease of production.

Similar to the original Levy \& Jaeger (2007), Zhan and Levy (2018)
focuses on information distribution at particular points in a sentence.
By contrast, Jain et al. (2018) examine word order across spoken
sentences in Hindi, a freer word order language than English, and find
that information density has no significant effect on word order. For
this paper, we focus on the sentence level instead of specific points,
following a method described in Yu et al. (2016).

Yu et al. (2016) challenges the UID hypothesis through examining an
entropy measure across sentence positions within the text portion of the
English-language British National Corpus (BNC). They partition the
corpus by sentence length in number of words. For each word position
\(X\) of sentences of length \(k\), they define \(w\) as a unique word
occurring in position \(X\). They define \(p(w)\) as the number of times
word \(w\) occurs in position \(X\) divided by the number of total words
that occur in position \(X\) i.e.~the number of sentences of length
\(k\). Then \(p(w)\) is the probability of obtaining word \(w\) by
choosing a word at random in position \(X\) in sentences of length
\(k\).

\[H(X) = \sum\limits_w p(w)\log\big(p(w)\big)\] With this measure, Yu et
al. compute the unigram entropy at each position of sentences of each
length within the corpus. The result of this method can be plotted for
each utterance length as an \emph{entropy curve}, which can be visually
compared across utterance length to observe the how the unigram entropy
changes across absolute positions in each of the utterances. Genzel \&
Charniak (2002) similarly examine a unigram entropy measure on
sentences, and found that entropy at the sentence level increases
linearly with sentence index within a corpus. UID applies this
uniformity of entropy rate in sentences to all levels of speech, and so
the Yu et al. method, which examines text at the word level, should find
an affine function at the word level.

@@

\section{Spoken data}\label{spoken-data}

The UID hypothesis predicts that information transmission rate will tend
towards uniformity in both speech and text. We begin by examining speech
to determine if we obtain the entropy curve shape we expect for spoken
communication. We begin with the same source as Levy \& Jaeger (2007)
and Jaeger (2010), the Switchboard corpus of adult telephone
conversations. We also examine child-adult conversations in the CHILDES
TalkBank (Brown 1973; MacWhinney 2014) corpora database of spoken
adult-child conversations in multiple languages. Children are not fully
developed speakers, so we want to compare the entropy curve we obtain by
computing over the utterances in the CHILDES corpora to the utterances
in the adult-adult Switchboard corpus.

\subsection{Methods}\label{methods}

@@

In the English CHILDES corpora. The entropy curves capture individual
variation across positions in utterances of the same length. This allows
us to directly observe and judge the amount of variation in words that
appear in an individual position of a sentence. For speech data, which
for the corpora in the CHILDES database consists of short and often
disconnected utterances across hours of recordings, the unigram entropy
measure is unaffected by context or lack thereof in utterances by the
adults and children in the corpora. We can directly compare any two
positions within utterances to determine the amount of uncertainty, and
therefore information, on average contained by words within that
position of utterances. We are applying the same approach as in Genzel
and Charniak (2002), but within sentences instead of across sentences.

@@

\subsection{Results \& Analysis}\label{results-analysis}

@@

\section{Written data}\label{written-data}

@@

\subsection{Methods}\label{methods-1}

@@

\subsection{Results and Analysis}\label{results-and-analysis}

@@

\begin{CodeChunk}
\begin{CodeOutput}
\begin{table}[H]
\centering
\begin{tabular}{rrllrrrr}
  \hline
 & X & feature & term & estimate & std.error & statistic & p.value \\ 
  \hline
1 &   1 & 83A & cosine & 1.84 & 0.01 & 178.22 & 0.00 \\ 
  2 &   2 & 95A & cosine & 1.90 & 0.01 & 170.98 & 0.00 \\ 
  3 &   3 & 81A & cosine & 1.51 & 0.01 & 153.70 & 0.00 \\ 
  4 &   4 & 97A & cosine & 1.58 & 0.01 & 136.81 & 0.00 \\ 
  5 &   5 & 144A & cosine & 0.88 & 0.01 & 74.43 & 0.00 \\ 
  6 &   6 & 138A & cosine & 0.40 & 0.01 & 46.12 & 0.00 \\ 
  7 &   7 & 87A & cosine & 0.33 & 0.01 & 39.91 & 0.00 \\ 
  8 &   8 & 143A & cosine & 0.37 & 0.01 & 39.74 & 0.00 \\ 
  9 &   9 & 82A & cosine & 0.03 & 0.01 & 3.23 & 0.00 \\ 
   \hline
\end{tabular}
\end{table}
\end{CodeOutput}
\end{CodeChunk}

@@

\section{Conclusions}\label{conclusions}

@@

\section{Acknowledgements}\label{acknowledgements}

@@

\section{References}\label{references}

\setlength{\parindent}{-0.1in} \setlength{\leftskip}{0.125in} \noindent

>>>>

\author{Josef Klafka \and Daniel Yurovsky \\
        \texttt{\{jklafka, yurovsky\}@uchicago.edu} \\
       Department of Psychology \\ University of Chicago}

@@

Perhaps the most important reason people talk and write to one another
is to give information. From Shannon (1948), we know that when
information is being communicated, the rate of information transmission
should be constant and as close as possible to the capacity of the
communication channel to optimally transmit the information.
({\textbf{???}}) introduce the \emph{uniform information density} (UID)
hypothesis, arguing that people unconsciously structure their speech and
writing to communicate information at a constant, optimal rate.
({\textbf{???}}) argue that speakers and writers should attempt to
communicate information as evenly as possible and as close to the
channel capacity as possible. Their evidence concerns the use or lack of
use of ``that''-complementizers in introducing English relative clauses.
When the word preceding the relative clause or the initial word of the
relative clause has high information content, then the authors argue
that speakers are more likely to use the complementizer. The authors use
adult-adult conversations from the Penn Treebank corpus.

UID has been applied broadly over the past decade, to determining
whether linguistic alignment takes place (Jaeger \& Snider, 2013),
Zipfian word length distributions (Piantadosi, Tily, \& Gibson, 2011),
communication efficiency (Mahowald, Fedorenko, Piantadosi, \& Gibson,
2013), dialogue and turn-taking (Xu \& Reitter, 2018) and the
significance of ambiguity in language (Piantadosi, Tily, \& Gibson,
2012), among other research. However, other recent work has contradicted
the UID hypothesis. Zhan \& Levy (2018) study Mandarin Chinese
classifier use for specific and general Mandarin classifiers. Specific
classifiers are specific to certain nouns, and UID would predict that
specific classifiers would appear when the production of the
corresponding noun is easier, to spread the information contained by the
classifier and noun less densely over time. General classifiers can be
applied to any noun and contain no special information content. Zhan and
Levy find that speakers use specific classifiers more often in cases
where the production of the corresponding noun is more difficult than
when the production is easier; speakers do not avoid unexpected peaks in
information content for their listeners, but instead maximize their ease
of production.

Similar to the original ({\textbf{???}}), Zhan \& Levy (2018) focuses on
information distribution at particular points in a sentence. By
contrast, Jain, Singh, Ranjan, Rajkumar, \& Agarwal (2018) examine word
order across spoken sentences in Hindi, a freer word order language than
English, and find that information density has no significant effect on
word order. For this paper, we focus on the sentence level instead of
specific points, following a method described in Yu, Cong, Liang, \& Liu
(2016).

Yu et al. (2016) challenges the UID hypothesis through examining an
entropy measure across sentence positions within the text portion of the
English-language British National Corpus (BNC, CITE). They partition the
corpus by sentence length in number of words. For each word position
\(X\) of sentences of length \(k\), they define \(w\) as a unique word
occurring in position \(X\). They define \(p(w)\) as the number of times
word \(w\) occurs in position \(X\) divided by the number of total words
that occur in position \(X\) i.e.~the number of sentences of length
\(k\). Then \(p(w)\) is the probability of obtaining word \(w\) by
choosing a word at random in position \(X\) in sentences of length
\(k\).

\[H(X) = \sum\limits_w p(w)\log\big(p(w)\big)\] With this measure, Yu et
al. (2016) compute the unigram entropy at each position of sentences of
each length within the corpus. The result of this method can be plotted
for each utterance length as an \emph{entropy curve}, which can be
visually compared across utterance length to observe the how the unigram
entropy changes across absolute positions in each of the utterances.
Genzel \& Charniak (2002) similarly examine a unigram entropy measure on
sentences, and found that entropy at the sentence level increases
linearly with sentence index within a corpus. UID applies this
uniformity of entropy rate in sentences to all levels of speech, and so
the Yu et al. (2016), which examines text at the word level, should find
an affine function at the word level.

@@

\hypertarget{spoken-data}{%
\section{Spoken data}\label{spoken-data}}

The UID hypothesis predicts that information transmission rate will tend
towards uniformity in both speech and text. We begin by examining speech
to determine if we obtain the entropy curve shape we expect for spoken
communication. We begin with the same source as ({\textbf{???}}) and
Jaeger (2010), the Switchboard corpus of adult telephone conversations.
We also examine child-adult conversations in the CHILDES TalkBank
(Brown, 1973; MacWhinney, 2014) corpora database of spoken adult-child
conversations in multiple languages. Children are not fully developed
speakers, so we want to compare the entropy curve we obtain by computing
over the utterances in the CHILDES corpora to the utterances in the
adult-adult Switchboard corpus.

\hypertarget{methods}{%
\subsection{Methods}\label{methods}}

@@

In the English CHILDES corpora. The entropy curves capture individual
variation across positions in utterances of the same length. This allows
us to directly observe and judge the amount of variation in words that
appear in an individual position of a sentence. For speech data, which
for the corpora in the CHILDES database consists of short and often
disconnected utterances across hours of recordings, the unigram entropy
measure is unaffected by context or lack thereof in utterances by the
adults and children in the corpora. We can directly compare any two
positions within utterances to determine the amount of uncertainty, and
therefore information, on average contained by words within that
position of utterances. We are applying the same approach as in Genzel
\& Charniak (2002), but within sentences instead of across sentences.

@@

\hypertarget{results-analysis}{%
\subsection{Results \& Analysis}\label{results-analysis}}

@@

\hypertarget{written-data}{%
\section{Written data}\label{written-data}}

@@

\hypertarget{methods-1}{%
\subsection{Methods}\label{methods-1}}

@@

\hypertarget{results-and-analysis}{%
\subsection{Results and Analysis}\label{results-and-analysis}}

@@

\begin{table}[tb]
\centering
\begin{tabular}{llrrrr}
  \hline
feature & term & estimate & std.error & statistic & p.value \\ 
  \hline
83A & cosine & 1.84 & 0.01 & 178.22 & 0.00 \\ 
  95A & cosine & 1.90 & 0.01 & 170.98 & 0.00 \\ 
  81A & cosine & 1.51 & 0.01 & 153.70 & 0.00 \\ 
  97A & cosine & 1.58 & 0.01 & 136.81 & 0.00 \\ 
  144A & cosine & 0.88 & 0.01 & 74.43 & 0.00 \\ 
  138A & cosine & 0.40 & 0.01 & 46.12 & 0.00 \\ 
  87A & cosine & 0.33 & 0.01 & 39.91 & 0.00 \\ 
  143A & cosine & 0.37 & 0.01 & 39.74 & 0.00 \\ 
  82A & cosine & 0.03 & 0.01 & 3.23 & 0.00 \\ 
   \hline
\end{tabular}
\end{table}

@@

\hypertarget{conclusions}{%
\section{Conclusions}\label{conclusions}}

@@

\hypertarget{acknowledgements}{%
\section{Acknowledgements}\label{acknowledgements}}

@@

\hypertarget{references}{%
\section{References}\label{references}}

\setlength{\parindent}{-0.1in} 
\setlength{\leftskip}{0.125in}

\noindent

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-brown1973}{}%
Brown, R. (1973). \emph{A first language: The early stages.} Harvard U.
Press.

\leavevmode\hypertarget{ref-genzel2002}{}%
Genzel, D., \& Charniak, E. (2002). Entropy rate constancy in text. In
\emph{Proceedings of the 40th annual meeting on association for
computational linguistics} (pp. 199--206). Association for Computational
Linguistics.

\leavevmode\hypertarget{ref-jaeger2010}{}%
Jaeger, T. F. (2010). Redundancy and reduction: Speakers manage
syntactic information density. \emph{Cognitive Psychology},
\emph{61}(1), 23--62.

\leavevmode\hypertarget{ref-jaeger2013}{}%
Jaeger, T. F., \& Snider, N. E. (2013). Alignment as a consequence of
expectation adaptation: Syntactic priming is affected by the prime's
prediction error given both prior and recent experience.
\emph{Cognition}, \emph{127}(1), 57--83.

\leavevmode\hypertarget{ref-jain2018}{}%
Jain, A., Singh, V., Ranjan, S., Rajkumar, R., \& Agarwal, S. (2018).
Uniform information density effects on syntactic choice in hindi. In
\emph{Proceedings of the workshop on linguistic complexity and natural
language processing} (pp. 38--48).

\leavevmode\hypertarget{ref-macwhinney2014}{}%
MacWhinney, B. (2014). \emph{The childes project: Tools for analyzing
talk, volume ii: The database}. Psychology Press.

\leavevmode\hypertarget{ref-mahowald2013}{}%
Mahowald, K., Fedorenko, E., Piantadosi, S. T., \& Gibson, E. (2013).
Info/information theory: Speakers choose shorter words in predictive
contexts. \emph{Cognition}, \emph{126}(2), 313--318.

\leavevmode\hypertarget{ref-piantadosi2011}{}%
Piantadosi, S. T., Tily, H., \& Gibson, E. (2011). Word lengths are
optimized for efficient communication. \emph{Proceedings of the National
Academy of Sciences}, \emph{108}(9), 3526--3529.

\leavevmode\hypertarget{ref-piantadosi2012}{}%
Piantadosi, S. T., Tily, H., \& Gibson, E. (2012). The communicative
function of ambiguity in language. \emph{Cognition}, \emph{122}(3),
280--291.

\leavevmode\hypertarget{ref-shannon1948}{}%
Shannon, C. E. (1948). A mathematical theory of communication.
\emph{Bell System Technical Journal}, \emph{27}(3), 379--423.

\leavevmode\hypertarget{ref-xu2018}{}%
Xu, Y., \& Reitter, D. (2018). Information density converges in
dialogue: Towards an information-theoretic model. \emph{Cognition},
\emph{170}, 147--163.

\leavevmode\hypertarget{ref-yu2016}{}%
Yu, S., Cong, J., Liang, J., \& Liu, H. (2016). The distribution of
information content in english sentences. \emph{arXiv Preprint
arXiv:1609.07681}.

\leavevmode\hypertarget{ref-zhan2018}{}%
Zhan, M., \& Levy, R. (2018). Comparing theories of speaker choice using
a model of classifier production in mandarin chinese. In
\emph{Proceedings of the 2018 conference of the north american chapter
of the association for computational linguistics: Human language
technologies, volume 1 (long papers)} (Vol. 1, pp. 1997--2005).
